### 2019-09-05 initial/notes.tex
add plot of locations of CS

First, we tackle the top integral. Here, the integrand is evaluated at
$\mu_+(\phi) = \eta \cos I + \sqrt{2\eta \sin I\p*{1 - \cos \phi}}$, so we can
plug this in and compute
\begin{align*}
    B_{top}\frac{2\alpha^2}{\epsilon} &= \int\limits_{2\pi}^{0}
            \mu(\alpha \mu + \cos I)\;\mathrm{d}\phi,\\
        &= -\int\limits_0^{2\pi}
            \p*{\eta \cos I + \sqrt{2\eta \sin I\p*{1 - \cos \phi}}}
                \p*{2\cos I + \sqrt{2\sin I\p*{1 - \cos \phi}/\eta}}
                \;\mathrm{d}\phi.
\end{align*}
Let's track the four terms in FOIL (first, outer, inner, last) order. (F)
evaluates to just $4\pi \eta \cos^2 I$. (O) evaluates to $\frac{\cos
I}{2}A_{sep} = 8\cos I\sqrt{\eta \sin I}$, and (I) twice that. Lastly, (L)
evaluates to $4\pi \sin I$. This agrees with our numerical check.

@@

Now, this turns out to be slightly inaccurate for $f > 0$ simply because our
$\mu_{sep}$ approximation is not so accurate for $\eta \gtrsim 0.2$, where the
top leg is significantly lower than the symmetric $\mu_{sep} = \eta \cos I \pm
\dots$ would predict. This would mean the two legs don't cancel as exactly, and
the capture probability increases, which is observed.

>>>>

First, we tackle the top integral. Here, the integrand is evaluated at
$\mu_+(\phi) = \eta \cos I + \sqrt{2\eta \sin I\p*{1 - \cos \phi}}$\footnote{
Bears noting that $\mu_{\pm} = \frac{\eta \cos I}{1 - \eta \sin I} \pm \dots$
significantly improves accuracy, it appears. Too many replacements to fix}, so
we can plug this in and compute
\begin{align*}
    B_{top}\frac{2\alpha^2}{\epsilon} &= \int\limits_{2\pi}^{0}
            \mu(\alpha \mu + \cos I)\;\mathrm{d}\phi,\\
        &= -\int\limits_0^{2\pi}
            \p*{\eta \cos I + \sqrt{2\eta \sin I\p*{1 - \cos \phi}}}
                \p*{2\cos I + \sqrt{2\sin I\p*{1 - \cos \phi}/\eta}}
                \;\mathrm{d}\phi.
\end{align*}
Let's track the four terms in FOIL (first, outer, inner, last) order. (F)
evaluates to just $4\pi \eta \cos^2 I$. (O) evaluates to $\frac{\cos
I}{2}A_{sep} = 8\cos I\sqrt{\eta \sin I}$, and (I) twice that. Lastly, (L)
evaluates to $4\pi \sin I$. This agrees with our numerical check.

@@
